Method quality control

### 2018-02-07 analysis/analyses/4-method_characterisation/7_quality_control.Rmd
rename experiment ids, and allow the number of citations to be updated to the google sheet

```{r message=F}
library(tidyverse)
library(dynalysis)
library(cowplot)

experiment("method_characteristics")

@@

g2 <- ggplot(methods_evaluated %>% mutate(ncitations = ifelse(ncitations == 0, 0.5, ncitations)), aes(date, ncitations)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_label_repel(aes(label = name)) +
    cowplot::theme_cowplot() +
    scale_y_log10() +
    labs(x = "Time", y = "Citations", title = "Citations over time")
g2

g3 <- ggplot(methods_evaluated %>% mutate(ncitations = ifelse(ncitations == 0, 0.5, ncitations)), aes(ncitations, qc_score)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_label_repel(aes(label = name)) +
    cowplot::theme_cowplot() +
    scale_x_log10() +
    labs(x = "Citations", y = "QC score", title = "QC score over # citations")
g3

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynalysis)
library(tidyverse)
library(cowplot)
```

```{r message=F}
experiment("4-method_characterisation")

@@

g2 <- ggplot(methods_evaluated %>% mutate(Citations = ifelse(Citations == 0, 0.5, Citations)), aes(date, Citations)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_label_repel(aes(label = name)) +
    cowplot::theme_cowplot() +
    scale_y_log10() +
    labs(x = "Time", y = "Citations", title = "Citations over time")
g2

g3 <- ggplot(methods_evaluated %>% mutate(Citations = ifelse(Citations == 0, 0.5, Citations)), aes(Citations, qc_score)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_label_repel(aes(label = name)) +
    cowplot::theme_cowplot() +
    scale_x_log10() +
    labs(x = "Citations", y = "QC score", title = "QC score over # citations")
g3
